\documentclass[a4paper]{article}

\usepackage[english]{babel}

\begin{document}
\section{Legal issues}

\subsection{List of packages and code used}

\begin{itemize}
\item Channels. https://github.com/django/channels/. BSD 3-clause "New" or "Revised" License.
\item Daphne. https://github.com/django/daphne/. BSD 3-clause "New" or "Revised" License.
\item asgiref. https://github.com/django/asgiref/. BSD 3-clause "New" or "Revised" License.
\item asgi\_redis. https://github.com/django/asgi\_redis/. BSD 3-clause "New" or "Revised" License.
\item vextab-div. 2012 Mohit Muthanna Cheppudira https://github.com/0xfe/vextab.
\item jquery. https://ajax.googleapis.com/ajax/libs/jquery/1.12.4/jquery.min.js. MIT License.
\item bootstrap. https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/js/bootstrap.min.js. MIT License.
\item django-autocomplete-light. https://github.com/yourlabs/django-autocomplete-light. MIT License.
\item django-bootstrap. https://github.com/dyve/django-bootstrap3. BSD 3-clause "New" or "Revised" License.
\item bootstrap.css (code). \\
https://maxcdn.bootstrapcdn.com/bootstrap/3.3.7/css/bootstrap.min.css. MIT License.
\end{itemize}

\subsection{Legal issues to consider for official release}

Licenses and copyright notices have to be retained from all the packages used. If used for commercial purposes, we will need to contact the owner of the vextab-div package. Redistribution with or without modification is permitted for packages under the BSD 3-clause License and MIT License. Under the BSD 3-clause license, neither the name of the copyright holder nor the names of its contributors may be used to endorse or promote our profuct without specific prior written permission.
\end{document}